---
title: Reddit Pilot 
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: false
    theme: cerulean
    toc_float: false
    code_folding: hide
---
  
  
```{r setup, include = F}
# load packages
library(tidyverse) 
library(knitr)
library(here)
library(anytime)
library(data.table)


opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F,  cache = T, fig.height = 4)
theme_set(theme_void())
source(here("exploratory_analyses/01_reddit_pilot/scripts/make_corr_plot.R"))


``` 

```{r}

tidy_data <- here("/exploratory_analyses/02_reddit_scaled_up/data/tidy/")

all_tidy <- map_df(list.files(tidy_data <- here("/exploratory_analyses/02_reddit_scaled_up/data/tidy/")
, full.names = T), read_csv, guess_max = 1000000) 

all_tidy_dt <- all_tidy %>%
  mutate(post_length = nchar(body_clean)) %>%
  select(-body, -body_clean, -title) %>%
  filter(created_utc >= "2017-09-01") %>%
  data.table()

```
## Descriptive statistics
### Subreddit size{.tabset}
####  Number of posts
```{r}
tidy_reddit_f <- all_tidy_dt %>%
  filter(author != "[deleted]") 

n_posts <- tidy_reddit_f %>%
  filter(text_type == "post") %>%
  count(subreddit,name =  "n_posts") %>%
  arrange(n_posts)

```

#### Number of comments
```{r}
n_comments <- tidy_reddit_f %>%
  filter(text_type == "comment") %>%
  count(subreddit,  name = "n_comments") %>%
  arrange(n_comments) 
```

####  Number of authors
```{r}
n_auth <- tidy_reddit_f %>%
  distinct(subreddit, author) %>%
  count(subreddit, name = "n_authors") %>%
  arrange(n_authors)

```

####  Number of authors with at least 5 comments/posts
```{r}
n_auth_large <- tidy_reddit_f %>%
  count(subreddit, author) %>%
  filter(n >= 5) %>%
  count(subreddit, name = "n_large_authors") %>%
  arrange(n_large_authors) 

```


### How many comments are there in each thread?
```{r}
tidy_reddit_f %>%
  count(subreddit, post_id) %>%
  ggplot(aes(x = n)) +
  geom_histogram(bins = 10) +
  scale_x_log10() +
  scale_y_log10() +
  xlab("N comments per thread") +
  facet_wrap(~subreddit) +
  theme_classic()

comments_per_thread <- tidy_reddit_f %>%
  count(subreddit, post_id) %>%
  group_by(subreddit) %>%
  summarize(mean_comments_per_thread = mean(n))
```

###  How many comments/posts does each author make?
```{r}
comments_per_author <- tidy_reddit_f %>%
  count(subreddit, author) %>%
  count(subreddit, n)  %>%
  group_by(subreddit) %>%
  summarize(mean_comments_per_author= mean(nn))

tidy_reddit_f %>%
  count(subreddit, author) %>%
  count(subreddit, n)  %>%
  ggplot(aes(x = nn)) +
  geom_histogram(bins = 100) +
  scale_x_log10() +
  scale_y_log10() +
  xlab("N posts per author") +
  facet_wrap(~subreddit) +
  theme_classic()
```

###  Comment length
```{r}
comment_length <- tidy_reddit_f %>%
  filter(text_type == "comment") %>%
  group_by(subreddit) %>%
  summarize(comment_length = mean(post_length, na.rm = T)) %>%
  arrange(comment_length)

```

## All subreddit-level variables
```{r}
subreddit_vars <- list(n_posts, n_comments, n_auth, n_auth_large, 
                       comments_per_thread, comments_per_author,comment_length) %>%
  reduce(full_join) 
#  mutate_at(c("n_posts",  "n_authors", "n_large_authors", 
 #                      "mean_comments_per_thread", "mean_comments_per_author","comment_length"), log)

make_corr_plot(subreddit_vars[,-1])

#write_csv(subreddit_vars, here("/exploratory_analyses/02_reddit_scaled_up/data/misc/subreddit_meta_data.csv"))
```

## Population over time
```{r, fig.width = 8}
birth_death <- tidy_reddit_f %>%
  group_by(subreddit, author) %>%
  summarize(birth = min(created_utc),
            death = max(created_utc),
            n = n())

birth_death_bin <- birth_death %>%
  #filter(n > 1) %>%
  mutate(birth_bin = lubridate::round_date(birth, "week"),
         death_bin = lubridate::round_date(death, "week")) %>%
  select(subreddit, birth_bin, death_bin) %>%
  gather("event", "value", -subreddit) %>%
  count(subreddit, event, value) %>%
  ungroup() 

total_births <- birth_death_bin %>%
  filter(event == "birth_bin") %>%
  group_by(subreddit)  %>%
  mutate(n = cumsum(n),
         event = "cum_births") %>%
  select(subreddit, value, n, event)  


total_deaths <- birth_death_bin %>%
  filter(event == "death_bin") %>%
  group_by(subreddit)  %>%
  mutate(n = -cumsum(n),
         event = "cum_deaths") %>%
  select(subreddit, value, n, event)  


pop_size <- birth_death_bin %>%
  left_join(total_births %>% rename(total_births = n) %>% select(-event),
            by = c("subreddit", "value")) %>%
  left_join(total_deaths %>% rename(total_deaths = n) %>% select(-event),
            by = c("subreddit", "value")) %>%
  mutate(n = total_births + total_deaths,
         event = "pop_size") %>%
  select(subreddit, event, value, n) 

pop_data <- birth_death_bin %>%
  bind_rows(pop_size) %>%
  bind_rows(total_births) %>%
  bind_rows(total_deaths)  %>%
  filter(event != "cum_births", event != "cum_deaths") %>%
  distinct()

ggplot(pop_data, aes(x = value, y = n, 
           color = event, group = event)) +
  geom_line() +
  facet_wrap(~subreddit, scale = "free_y") +
  theme_classic()
```


## Text analysis
### At thread level

* A thread with more comments has longer comments
* As the community gets older there are fewer comments per thread
* As a community gets older, comments get shorter
* As popluation size increases, comment length increases, but num comments decreases.

```{r, eval = F}
reddit_text <- tidy_reddit_f %>%
  filter(text_type == "comment")

targ_authors <- reddit_text %>%
  count(subreddit, author) %>% 
  filter(n >= 50)

pop_data_wide <- pop_data %>%
  filter(event == "pop_size") 
  
length_over_time <- reddit_text %>%
  group_by(subreddit, post_id) %>%
  summarize(log_n_comments = log(n()),
            log_mean_length = log(mean(post_length)),
            first_comment = min(created_utc),
            first_comment_time_num = as.numeric(first_comment)) %>%
  mutate(first_comment_bin = lubridate::round_date(first_comment, "month")) %>%
  left_join(pop_data %>% filter(event == "pop_size") , by = c("subreddit", "first_comment_bin" = "value"))

length_over_time_tidy <- length_over_time %>%
  select(subreddit, log_mean_length, first_comment_time_num, n) %>%
  rename(population_size = n) %>%
  group_by(subreddit) %>%
  nest() %>%
  mutate(temp = map(data, ~tidy(cor.test(.$population_size, .$log_mean_length)))) %>%
  select(-data) %>%
  unnest() %>%
  left_join(n_auth_large) %>%
  left_join(n_auth) %>%
  ungroup() %>%
  mutate(subreddit = fct_reorder(subreddit, n_authors))

ggplot(length_over_time_tidy, aes(x = n_large_authors, y = estimate)) +
  geom_smooth(method = "lm") +
  scale_x_log10() +
  geom_label(aes(label = subreddit)) +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), alpha =  .2) +
  theme_classic()

# n_comments_time_tidy <- length_over_time %>%
#   select(subreddit, log_n_comments, first_comment_time_num, n) %>%
#   rename(population_size = n) %>%
#   group_by(subreddit) %>%
#   nest() %>%
#   mutate(temp = map(data, ~tidy(cor.test(.$population_size, .$log_n_comments)))) %>%
#   select(-data) %>%
#   unnest()  %>%
#   left_join(n_auth_large) %>%
#   ungroup() %>%
#   mutate(subreddit = fct_reorder(subreddit, n_large_authors))
# 
# ggplot(n_comments_time_tidy, aes(x = n_large_authors, y = estimate)) +
#   geom_smooth(method = "lm") +
#   #scale_x_log10() +
#   geom_hline(aes(yintercept = 0), linetype = 2) +
# 
#   geom_pointrange(aes(ymin = conf.low, ymax = conf.high), alpha =  .2) +
#   theme_classic()



```

### At individual level

Weak effect of time in community - longer in community, write less. 
```{r, eval = F}
nested_authors_text <- reddit_text %>% 
  filter(author %in% targ_authors$author) %>%
  group_by(subreddit, author) %>% 
  mutate(birth = min(created_utc)) %>%
  arrange(author, created_utc) %>%
  mutate(comment_num = 1:n(),
         time_since_birth = as.numeric(created_utc - birth)) %>%
  ungroup() %>% 
  select(subreddit, author, comment_num, time_since_birth, created_utc, post_length) %>%
  group_by(subreddit, author) %>%
  nest()

score_corrs <- nested_authors_text %>%
  mutate(corr_pearson_tsb = map(data, ~cor(.$post_length , .$time_since_birth, method = "pearson")),
         corr_spearman_comment_num = map(data, ~cor(.$post_length , .$comment_num, method = "spearman"))) %>%
  select(-data) %>%
  unnest() %>%
  gather("measure", "value", -subreddit, -author)

mean_values <- score_corrs %>%
  group_by(subreddit, measure) %>%
  tidyboot::tidyboot_mean(col = value, na.rm = T)

ggplot(score_corrs, aes(x = value)) +
  geom_histogram() +
  geom_vline(data = mean_values, 
             aes(xintercept = mean), 
             color = "red", linetype = 2) +
  facet_grid(measure ~ subreddit) +
  theme_classic()

kable(mean_values)
```



```{r, eval = F}
## Do scores get higher the longer you're in the community?

#Weak evidence if you look at folks who have at least 50 posts.
targ_authors <- tidy_reddit_f %>%
  count(subreddit, author) %>% 
  filter(n >= 50)

nested_authors <- tidy_reddit_f %>% 
  right_join(targ_authors %>% select(-n)) %>%
  filter(text_type == "comment") %>%
  group_by(subreddit, author) %>% 
  mutate(birth = min(created_utc)) %>%
  arrange(author, created_utc) %>%
  mutate(comment_num = 1:n(),
         time_since_birth = as.numeric(created_utc - birth)) %>%
  ungroup() %>% 
  select(subreddit, author, comment_num, time_since_birth, created_utc, score) %>%
  group_by(subreddit, author) %>%
  nest()

score_corrs <- nested_authors %>%
  mutate(corr_pearson_tsb = map(data, ~cor(.$score , .$time_since_birth, method = "pearson")),
         corr_spearman_comment_num = map(data, ~cor(.$score , .$comment_num, method = "spearman"))) %>%
  select(-data) %>%
  unnest() %>%
  gather("measure", "value", -subreddit, -author)

mean_values <- score_corrs %>%
  group_by(subreddit, measure) %>%
   tidyboot::tidyboot_mean(col = value, na.rm = T)

ggplot(score_corrs, aes(x = value)) +
  geom_histogram() +
  geom_vline(data = mean_values, 
             aes(xintercept = mean), 
             color = "red", linetype = 2) +
  facet_grid(measure ~ subreddit) +
  theme_classic()

kable(mean_values)
```

```{r, eval = F}
#HYPOTHESES:

#* As population size increases, complexity of norms decreases (moderated by population structure, prop new, etc)
#* Social variables influence alignment: people who are responded to more introduce more norms
#* Norms of larger communities change more quickly and are less coherent across individuals
#* Topic entropy as a mediating factor
#* what are the social conditions for the emergence of a new words, and are those facilitated or hindered by population size
```

