---
title: Similarity over time
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: false
    theme: cerulean
    toc_float: false
    code_folding: hide
---
  
  
```{r setup, include = F}
# load packages
library(tidyverse) 
library(knitr)
library(here)
library(anytime)
library(tidytext)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F,  cache = T, fig.height = 4)
theme_set(theme_void())
source(here("exploratory_analyses/01_reddit_pilot/scripts/make_corr_plot.R"))
``` 

## Meta-data
```{r, fig.width = 10, fig.height = 5}

pairwise_topic_jsd_path <- here("/exploratory_analyses/02_reddit_scaled_up/data/jsd_over_community_time/")

over_community_time <- map_df(list.files(pairwise_topic_jsd_path, full.names = T), ~{read_csv(.x) %>% mutate(subreddit = .x)}) %>%
  mutate(subreddit = str_replace(subreddit, paste0(pairwise_topic_jsd_path, "/"), ""),
         subreddit = str_replace(subreddit, "_jsd_over_community_time.csv", ""))

META_DATA <-  here("/exploratory_analyses/02_reddit_scaled_up/data/misc/subreddit_meta_data.csv")
subreddit_meta <- read_csv(META_DATA) %>%
  mutate(subreddit = case_when(subreddit == "TheRedPill" ~ "redpill", TRUE ~ subreddit)) %>%
  select(-n_large_authors) %>%
  arrange(n_authors) %>%
  select(subreddit, n_authors, everything())

kable(subreddit_meta)
make_corr_plot(log(subreddit_meta[,-1]))
```

## JSD over community time{.tabset}
### post similarity over commuity time
```{r, fig.width = 10, fig.height = 8.5}
over_community_time_with_meta <- over_community_time %>%
  left_join(subreddit_meta) %>%
  mutate(subreddit = fct_reorder(subreddit, n_authors))

ggplot(over_community_time_with_meta, 
       aes(x = group, y = mean_jsd )) +
  facet_wrap(~subreddit, scale = "free") +
  geom_point(aes(size = n), alpha = .3) +
  xlab("Date (in weeks)") +
  ylab("Mean JSD") +
  ggtitle("Post similarity over community time") +
  geom_smooth(color = "blue" ) +
  geom_smooth(method = "lm",color = "red" ) +
  theme_classic(base_size = 14)
```

### slope and demographic variables 
```{r, fig.width = 10, fig.height = 8.5}
jsd_time_correlation <- over_community_time_with_meta %>%
  group_by(subreddit) %>%
  nest() %>%
  mutate(temp = map(data, ~tidy(cor.test(as.numeric(.$group), .$mean_jsd))))  %>%
  select(-data) %>%
  unnest() %>%
  left_join(subreddit_meta)

jsd_time_correlation %>%
  select(1,2,6,7, 10:15) %>%
  gather("measure", "value", -1:-4) %>%
  ggplot(aes(x = value, y = estimate))+
  geom_label(aes(label = subreddit)) +
  geom_smooth(method = "lm") +
  facet_wrap(~measure, scales = "free_x") +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), alpha =  .2) +
  theme_classic()
```

### slope and demographic variables (log x) 

```{r, fig.width = 10, fig.height = 8.5}
jsd_time_correlation %>%
  select(1,2,6,7, 10:15) %>%
  gather("measure", "value", -1:-4) %>%
  ggplot(aes(x = value, y = estimate))+
  geom_label(aes(label = subreddit)) +
  geom_smooth(method = "lm") +
  scale_x_log10() +
  facet_wrap(~measure, scales = "free_x") +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), alpha =  .2) +
  theme_classic()

```

## JSD over individual time{.tabset}

__pink__ - mean distance of current post to all other posts in that time period in community;

__green__ - distance to previous author post

```{r}
PAIRWISE_TOPIC_JSD <- here("/exploratory_analyses/02_reddit_scaled_up/data/jsd_nth_post/")


nth_post_data <- map_df(list.files(PAIRWISE_TOPIC_JSD, full.names = T), ~{read_csv(.x) %>% mutate(subreddit = .x)}) %>%
  mutate(subreddit = str_replace(subreddit, paste0(PAIRWISE_TOPIC_JSD, "/"), ""),
         subreddit = str_replace(subreddit, "_jsd_nth_post.csv", ""))

over_individual_time <- nth_post_data  %>%
  select(author, nth_post, previous_author_JSD, current_community_JSD, subreddit) %>%
  gather("measure", "value", -nth_post, -subreddit, -author)
```


###  n = all
```{r, fig.width = 10, fig.height = 7}
over_individual_time_ms <- over_individual_time %>%
  group_by(subreddit, nth_post, measure) %>%
  summarize(mean_JSD = mean(value, na.rm = T),
            n = n()) %>%
    left_join(subreddit_meta) %>%
  ungroup() %>%
  mutate(subreddit = fct_reorder(subreddit, n_authors))

over_individual_time_ms %>%
  ggplot(aes(x = nth_post, y = mean_JSD, group = measure, color = measure)) +
  geom_point() +
  geom_smooth() +
  ggtitle("Post similarity over indvidual time (with community reference)") +
  xlab("Nth post") +
   facet_wrap(~subreddit, scales = "free_y") +
  ylab("Mean JSD") +
  theme_classic()
```


###  n >= 50
```{r, fig.width = 10, fig.height = 7}
over_individual_time_ms <- over_individual_time %>%
  group_by(subreddit, nth_post, measure) %>%
  summarize(mean_JSD = mean(value, na.rm = T),
            n = n()) %>%
  filter(n >= 50) %>%
  left_join(subreddit_meta) %>%
  ungroup() %>%
  mutate(subreddit = fct_reorder(subreddit, n_authors))


over_individual_time_ms %>%
  ggplot(aes(x = nth_post, y = mean_JSD, group = measure, color = measure)) +
  geom_point() +
  geom_smooth() +
  ggtitle("Post similarity over indvidual time (with community reference)") +
  xlab("Nth post") +
  ylab("Mean JSD") +
  facet_wrap(~subreddit, scales = "free_y") +
  theme_classic()
```


## slope and population variables{.tabset}

### 1-25 posts
```{r, fig.width = 10, fig.height = 7}

over_individual_time_ms <- over_individual_time %>%
  filter(nth_post <= 25) %>%
  group_by(subreddit, nth_post, measure) %>%
  summarize(mean_JSD = mean(value, na.rm = T),
            n = n()) %>%
  group_by(subreddit, measure) %>%
  nest() %>%
  mutate(temp = map(data, ~tidy(cor.test(.$nth_post, .$mean_JSD))))  %>%
  select(-data) %>%
  unnest() %>%
  left_join(subreddit_meta)


over_individual_time_ms %>%
  select(1,2,3, 7, 8, 11:16) %>%
  gather("measure2", "value", -1:-5) %>%
  ggplot(aes(x = value, y = estimate, group = measure, color = measure))+
  geom_label(aes(label = subreddit)) +
  geom_smooth(method = "lm") +
  facet_wrap(~measure2, scales = "free_x") +
  scale_x_log10()  +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), alpha =  .2) +
  theme_classic()
```

### 1-50 posts
```{r, fig.width = 10, fig.height = 7}

over_individual_time_ms <- over_individual_time %>%
  filter(nth_post <= 50) %>%
  group_by(subreddit, nth_post, measure) %>%
  summarize(mean_JSD = mean(value, na.rm = T),
            n = n()) %>%
  group_by(subreddit, measure) %>%
  nest() %>%
  mutate(temp = map(data, ~tidy(cor.test(.$nth_post, .$mean_JSD))))  %>%
  select(-data) %>%
  unnest() %>%
  left_join(subreddit_meta)


over_individual_time_ms %>%
  select(1,2,3, 7, 8, 11:16) %>%
  gather("measure2", "value", -1:-5) %>%
  ggplot(aes(x = value, y = estimate, group = measure, color = measure))+
  geom_label(aes(label = subreddit)) +
  geom_smooth(method = "lm") +
  facet_wrap(~measure2, scales = "free_x") +
  scale_x_log10()  +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), alpha =  .2) +
  theme_classic()
```


### 1-100 posts
```{r, fig.width = 10, fig.height = 7}

over_individual_time_ms <- over_individual_time %>%
  filter(nth_post <= 100) %>%
  group_by(subreddit, nth_post, measure) %>%
  summarize(mean_JSD = mean(value, na.rm = T),
            n = n()) %>%
  group_by(subreddit, measure) %>%
  nest() %>%
  mutate(temp = map(data, ~tidy(cor.test(.$nth_post, .$mean_JSD))))  %>%
  select(-data) %>%
  unnest() %>%
  left_join(subreddit_meta)


over_individual_time_ms %>%
  select(1,2,3, 7, 8, 11:16) %>%
  gather("measure2", "value", -1:-5) %>%
  ggplot(aes(x = value, y = estimate, group = measure, color = measure))+
  geom_label(aes(label = subreddit)) +
  geom_smooth(method = "lm") +
  facet_wrap(~measure2, scales = "free_x") +
  scale_x_log10()  +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), alpha =  .2) +
  theme_classic()
```


